\documentclass[10pt, letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
    \geometry{
        top=0.8in,
        bottom=0.8in,
        left=0.9in,
        right=0.9in
    }

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Xiaodong Hu}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}


% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
% \renewenvironment{itemize}{
%   \begin{list}{}{
%     \setlength{\leftmargin}{1.5em}
%   }
% }{
%   \end{list}
% }


\pagestyle{empty} % no title
\begin{document}
\vspace{-2in}
% place name at left
{\huge\bf\name}
\hfill\\

\begin{minipage}{0.5\linewidth}
    \begin{tabular}{ll}
        & 330L Higgins Hall\\
        & Boston College\\
        & 140 Commonwealth Ave, MA 02467
    \end{tabular}
\end{minipage}
\begin{minipage}{0.5\linewidth}
  \begin{tabular}{ll}
    Phone: & (1) 857-272-7073 \\
    Email: & \href{mailto:xiaodong.hu@bc.edu}{\tt xiaodong.hu@bc.edu} \\
    Homepage: & \href{https://xiaodong-hu.github.io/}{\tt https://xiaodong-hu.github.io/} \\
  \end{tabular}
\end{minipage}

\makebox[\linewidth]{\rule{\linewidth}{1.0pt}}

\vspace{-0.5em}
\section*{Education}
\begin{minipage}{0.55\linewidth}
    \begin{tabular}{ll}
        & {\bf Boston College} \\
        & 2018-2024 (expected)        
    \end{tabular}
\end{minipage}
\begin{minipage}{0.45\linewidth}
    \begin{tabular}{ll}
        & Ph.D in Condensed Matter Theory\\
        & Advisor: \emph{Ying Ran}
    \end{tabular}
\end{minipage}
\\[1em]
\begin{minipage}{0.55\linewidth}
    \begin{tabular}{ll}
        & {\bf University of Science and Technology of China}\\
        & 2014-2018 
    \end{tabular}
\end{minipage}
\begin{minipage}{0.45\linewidth}
    \begin{tabular}{ll}
        & B.S. in Theoretical Physics\\
        & { }
    \end{tabular}
\end{minipage}



\section*{Research Interests}
My research is primarily focused on exploring the intricate emergent phenomena in strongly-correlated systems, with a particular emphasis on the interplay of symmetry and topology, such as fractional Chern insulators (lattice analogue of fractional Quantum Hall effect), Kitaev materials, and high-$T_c$ superconductors. Both analytic methods and numerical simulations are used in my research.

\section*{Publications/Preprints}
\begin{itemize}
    \item \underline{X-D. Hu}, D. Xiao, and Y. Ran, \href{https://arxiv.org/abs/2312.00636v2}{\emph{Hyperdeterminants and Composite Fermion States in Fractional Chern Insulators}},  (submitted to PRX)
    \item \underline{X-D. Hu}, J-H. Han, and Y. Ran, \href{https://journals.aps.org/prb/abstract/10.1103/PhysRevB.108.L041106}{\emph{Supercurrent-induced anomalous thermal Hall effect as a new probe to superconducting gap anisotropy}}, Phys. Rev. B \textbf{108}, L041106 (2023)
    \item \underline{X-D. Hu}, and Y. Ran, \href{https://journals.aps.org/prb/abstract/10.1103/PhysRevB.106.125136}{\emph{Engineering chiral topological superconductivity in twisted Ising superconductors}}, Phys. Rev. B \textbf{106}, 125136 (2022)
    \item F. Bahrami, \underline{X-D. Hu}, Y. Du, O. I. Lebedev, C. Wang, H. Luetkens, G. Fabbris, M. J. Graf, D. Haskel, Y. Ran, and F. Tafti, \href{https://www.science.org/doi/full/10.1126/sciadv.abl5671}{\emph{First demonstration of tuning between the Kitaev and Ising limits in a honeycomb lattice}}, Sci. Adv. \textbf{8}, eabl5671 (2022)
\end{itemize}


\section*{Presentations}
\begin{itemize}
    \item \emph{Engineering Chiral Topological Superconductivity in Twisted Ising Superconductors}, Talk, APS March Meeting, 2023
    \item \emph{Supercurrent-induced anomalous thermal Hall effect as a new probe to superconducting gap anisotropy}, Talk, online APS March Meeting, 2023
\end{itemize}

\section*{Techniques}
    \begin{tabular}{ll}
        Programming Languages & Julia, Rust, Python, Mathematica, C++, Bash.\\
        DFT Tools & Quantum Espresso, ELK\\
    \end{tabular}

\section*{Developed Packages}
    \begin{itemize}
        \item \texttt{FCI.jl}, includes \texttt{LLL.jl}, \texttt{MODEL.jl}, \texttt{FCB\_ED.jl}, \texttt{CF.jl}, \texttt{CF\_MF.jl}, \texttt{CF\_TDHF.jl}, \texttt{CF\_PROJWFC.jl}, etc. for our big project of the projective construction of fractional Chern insulators.
        \item \texttt{TightBinding.jl} and \texttt{TightBindMeanField.jl} for tight-binding model construction, quantum transport study, and interface to \texttt{wannier90}.
    \end{itemize}

    % \vspace{0.5em}
    % I have developped julia packages \texttt{TightBinding.jl} for extracting tightbinding models from Quantum Espresso, and \texttt{TightBindingMeanField.jl} for mean-field calculation for cluster of crystals 


\section*{Teaching Experiences}
    During my time at Boston College, I have served as a Teaching Assistant for several graduate courses, including Classical Mechanics, Electrodynamics, Quantum Mechanics I/II, Statistical Mechanics I/II, and Particle Physics. In the summer of 2023, I also served as an instructor for an undergraduate course, Introduction to Physics I/II.



% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today 
  \end{footnotesize}
\end{center}

\end{document}
